\paperTitle

### 2014-05-17 doc/icml2014/directed.tex
Updated intro figure, added exclusive views figure
some changes near beginning - bottlenecks, etc.
terninology change

%In this section, we will develop a consistent parameter estimate for a class of directed graphical models.
%The conditional moments $\mOpp{v}{i} \eqdef \Pr(x_v \mid h_i)$
%recovered from {\TensorFactorize}, are not the underlying parameters.
  %Once we recover the conditional moments $\mOpp{v}{j} \eqdef \Pr(x_v
  %| h_j)$ for some $v, j$, we present a systematic approach to learn the
  %conditional probability tables for every clique for a class of directed
  %graphical models.
Having recovered conditional moments $\mOpp{v}{i} \eqdef \Pr(x_v \mid h_i)$,
we now seek to compute the marginal distribution of sets of hidden variables
$Z_S \eqdef \Pr(\bh_S)$.
%taking us one step closer to the actual model parameters.
%For clarity, we derive our algorithm in the infinite data limit,
%although the actual algorithm works with estimates.

@@

  %Section~\ref{sec:directedGeneral} will describe the algorithm in full generality.
%For ease of exposition we make the following simplifications to our presentation:
%(i) we describe our algorithm entirely in the context of directed
  %graphical models, though it generalizes to undirected models;
%(iii) we present the algorithm solely in terms of linear algebraic operations;
  %\sectionref{piecewise} provides a statistically
  %more efficient estimator using composite likelihood.

@@

\algorithmref{learnclique} summarizes the procedure, \LearnClique.
Given $Z_S$, the conditional probability tables for $S$ can easily be
obtained via renormalization.
\begin{theorem}[Hidden marginals from exclusive views]
If $S \subseteq \bx$ is a subset of hidden variables with the exclusive views property,
then \algorithmref{learnclique} recovers the marginals $Z_S = \Pr(\bh_S)$.
\end{theorem}

\begin{algorithm}
  \caption{\LearnClique~(pseudoinverse version)}
  \label{algo:learnclique}
  \begin{algorithmic}
    \REQUIRE Hidden subset $S = \{ h_{i_1}, \dots, h_{i_m} \}$ with exclusive views $\sV = \{ x_{v_1}, \dots, x_{v_m} \}$
    and $\{\mOpp{v_1}{i_i}\pinv\}$ % (\definitionref{exclusive-views})
    \ENSURE Marginal distribution $Z_S = \Pr(\bh_S)$.
      %\STATE Identify exclusive views $\Sx{\sV} = \{x_{v_1}, \dots, x_{v_m}\}$.
      \STATE Return $\mH_S \gets \mO_{\sV}( \mOpp{v_1}{i_i}\pinv, \dots, {\mOpp{v_m}{i_m}}\pinv )$.
  \end{algorithmic}
\end{algorithm}

>>>>

\begin{figure}
  \centering
  \subfigure[Three-view mixture model] {
    \includegraphics[width=0.45\columnwidth]{figures/three-view.pdf}
    \label{fig:three-view}
  }
  \subfigure[Exclusive views]{
    \includegraphics[width=0.45\columnwidth]{figures/exclusive-views.pdf}
    \label{fig:exclusive-views}
  }

  \caption{(a) The canonical three-view mixture model can be estimated consistently
  using tensor factorization \citep{anandkumar13tensor}.
  (b) An example of exclusive views for a bi-dependent subset $S$.
  }
\end{figure}

%In this section, we will develop a consistent parameter estimate for a class of directed graphical models.
%The conditional moments $\mOpp{v}{i} \eqdef \Pr(x_v \mid h_i)$
%recovered from {\TensorFactorize}, are not the underlying parameters.
  %Once we recover the conditional moments $\mOpp{v}{j} \eqdef \Pr(x_v
  %| h_j)$ for some $v, j$, we present a systematic approach to learn the
  %conditional probability tables for every clique for a class of directed
  %graphical models.
Having recovered conditional moments $\mOpp{v}{i} \eqdef \Pr(x_v \mid h_i)$,
we now seek to compute the marginal distribution of sets of hidden variables
$Z_S \eqdef \Pr(\bh_S)$.
%taking us one step closer to the actual model parameters.

@@

@@

\algorithmref{learnclique} summarizes the procedure, \LearnMarginals.
Given $Z_S$, the conditional probability tables for $S$ can easily be
obtained via renormalization.
\begin{theorem}[Hidden marginals from exclusive views]
If $S \subseteq \bx$ is a subset of hidden variables with the exclusive views property,
then \algorithmref{learnclique} recovers the marginals $Z_S = \Pr(\bh_S)$.
\end{theorem}

\begin{algorithm}
  \caption{\LearnMarginals~(pseudoinverse version)}
  \label{algo:learnMarginals}
  \begin{algorithmic}
    \REQUIRE Hidden subset $S = \{ h_{i_1}, \dots, h_{i_m} \}$ with exclusive views $\sV = \{ x_{v_1}, \dots, x_{v_m} \}$
    and conditional moments $\mOpp{v_j}{i_j} = \Pr(x_{v_i} \mid h_{i_j})$
    \ENSURE Marginals $Z_S = \Pr(\bh_S)$.
      %\STATE Identify exclusive views $\Sx{\sV} = \{x_{v_1}, \dots, x_{v_m}\}$.
      \STATE Return $\mH_S \gets \mO_{\sV}( \mOpp{v_1}{i_i}\pinv, \dots, {\mOpp{v_m}{i_m}}\pinv )$.
  \end{algorithmic}
\end{algorithm}

### 2014-05-17 doc/icml2014/undirected.tex
terninology change

If we knew $\mu_{a,\sN(a)} \eqdef \E[\phi_{a,\sN(a)}(a,\sN(a))]$,
then we would be able to optimize the pseudolikelihood objective again without
having access to any labeled data.
%The pseudolikelihood also replaces the log-partition function
%  $A(\theta)$ with a sum over the variables in the neighborhood:
%  $A_a(\theta; x_{\sN(a)}) = \sum_{a' \in \{a\} \union \sN(a)}
%  \exp(\theta^\top\phi_{\sN(a)}(a'))$.
Note that $\{a\}\cup\sN(a)$ in general do not form a clique.
Fortunately, \lemmaref{bottleneck-views} holds for all biconnected subgraphs.
We can break $\{a\}\cup\sN(a)$ into a collection of 
  % PL: this is not necessary
  %thus the uniformly bottlenecked assumption alone is not sufficient to
  %guarantee exclusive views for each variable in that subgraph.
%However, when we do have exclusive views for each neighborhood, as in
  \figureref{examples-mrf},
  Therefore, we can adapt our algorithm ($\LearnClique$) to estimate all marginals of the form $Z_{a,\sN(a)} \eqdef \Pr(a,\sN(a))$,
  from which we can compute the features $\mu_{a,\sN(a)}$,
  and optimize \equationref{pseudolikelihood} to obtain a consistent estimate of $\theta$.

>>>>

If we knew $\mu_{a,\sN(a)} \eqdef \E[\phi_{a,\sN(a)}(a,\sN(a))]$,
then we would be able to optimize the pseudolikelihood objective again without
having access to any labeled data.
%The pseudolikelihood also replaces the log-partition function
%  $A(\theta)$ with a sum over the variables in the neighborhood:
%  $A_a(\theta; x_{\sN(a)}) = \sum_{a' \in \{a\} \union \sN(a)}
%  \exp(\theta^\top\phi_{\sN(a)}(a'))$.
Note that $\{a\}\cup\sN(a)$ in general do not form a clique.
Fortunately, \lemmaref{bottleneck-views} holds for all biconnected subgraphs.
We can break $\{a\}\cup\sN(a)$ into a collection of 
  % PL: this is not necessary
  %thus the uniformly bottlenecked assumption alone is not sufficient to
  %guarantee exclusive views for each variable in that subgraph.
%However, when we do have exclusive views for each neighborhood, as in
  \figureref{examples-mrf},
  Therefore, we can adapt our algorithm ($\LearnMarginals$) to estimate all marginals of the form $Z_{a,\sN(a)} \eqdef \Pr(a,\sN(a))$,
  from which we can compute the features $\mu_{a,\sN(a)}$,
  and optimize \equationref{pseudolikelihood} to obtain a consistent estimate of $\theta$.
